EuPPollNet: A European database of plant-pollinator networks

### 2024-08-20 Manuscript/EuPPollNet_Ms.qmd
Minor edits

#Plot
p3 = ggplot(data_long, aes(x = Variable, y = Value, fill = Pollinator_order)) + 
geom_bar(stat = "identity", width = 0.7) +
theme_classic() +
scale_fill_viridis(discrete=TRUE, direction = -1, name="Pollinator order") +
xlab(NULL) +
ylab("Percentage") + 
scale_y_continuous(labels = percent_format(), expand = c(0, 0)) +
theme(axis.text = element_text(size=6), 
     axis.title.y = element_text(face = "bold", size = 7, vjust = -2),  
     axis.title.x = element_text(face="bold", size = 7),
     legend.position = "top",
     legend.title = element_text(size = 5, face = "bold"),
     legend.text = element_text(size = 5),
     legend.key.size = unit(3, "mm"),
     legend.margin=margin(0,0,0,0),
     legend.box.margin=margin(-8,-5,-5,-5)) +
guides(fill=guide_legend(nrow=2,byrow=TRUE))+
ggtitle("(c)") +
theme(plot.title = element_text(size = 10,hjust = -0.3, vjust = -6)) +
scale_x_discrete(labels = c("Species\n (2172)", "Interactions\n (358,049)"))

>>>>

#Plot
p3 = ggplot(data_long, aes(x = Variable, y = Value, fill = Pollinator_order)) + 
geom_bar(stat = "identity", width = 0.7) +
theme_classic() +
scale_fill_viridis(discrete=TRUE, direction = -1, name="Pollinator order") +
xlab(NULL) +
ylab("Percentage") + 
scale_y_continuous(labels = percent_format(), expand = c(0, 0)) +
theme(axis.text = element_text(size=6), 
     axis.title.y = element_text(face = "bold", size = 7, vjust = -2),  
     axis.title.x = element_text(face="bold", size = 7),
     legend.position = "top",
     legend.title = element_text(size = 5, face = "bold"),
     legend.text = element_text(size = 5),
     legend.key.size = unit(3, "mm"),
     legend.margin=margin(0,0,0,0),
     legend.box.margin=margin(-8,-5,-5,-5)) +
guides(fill=guide_legend(nrow=2,byrow=TRUE))+
ggtitle("(c)") +
theme(plot.title = element_text(size = 10,hjust = -0.3, vjust = -6)) +
scale_x_discrete(labels = c("Species\n (2,172)", "Interactions\n (358,049)"))
